\texttt{davos}: The Python package smuggler

### 2022-08-10 paper/main.tex
software functionalities subsections
updates to first paragraph

% --------------------------------------------- MOTIVATION & SIGNIFICANCE ----------------------------------------------
\section{Motivation and significance}
Modern scientific research often involves writing code for a variety of purposes throughout the research process, from designing experiments, to analyzing and visualizing data, to presenting findings or techniques via tutorials or public demos. 
One requirement common to nearly all research-related code it that its behavior and/or outputs must remain consistent and predictable every time it is run, both over time and across users. 
For example, this stability can be critical to ensuring that data are collected under constant conditions (e.g., across recordings, trials, or subjects) and that statistical analyses yield accurate, reliable results. 
Additionally, modern open science practices encourage sharing code and data publicly to enable others to explore, reproduce, learn from, and build upon existing work. 
Scientists, researchers, and educators may seek to share research code with audiences that have a wide range of scientific and technical backgrounds, including collaborators, students, the broader scientific community, and the general public.

@@

\subsection{Software Functionalities}
% Present the major functionalities of the software.

>>>>

% --------------------------------------------- MOTIVATION & SIGNIFICANCE ----------------------------------------------
\section{Motivation and significance}
Modern scientific research often entails writing software code for a wide variety of purposes throughout the scientific process:
researchers across disciplines design and implement experimental paradigms; collect, process, and analyze large datasets; create visualizations for presentations and publications; and share their findings and techniques with peers, students, and the broader public through tutorials, demos, workshops, and classes.
However, one requirement common to nearly all research-related code is that it behave consistently and predictably every time it is run, both over time and across different users.
This stability can be crucial to ensuring, for example, that data are collected under the same conditions (e.g., across recordings, trials, or subjects) over multiple months or years, and can be processed and analyzed consistently by collaborators across multiple institutions or countries.
Additionally, modern open science practices encourage sharing research code and data publicly to enable others to explore, reproduce, learn from, and build upon existing work.
Much of the benefit afforded by freely available research code relies on users ability to execute it and achieve the same result as its original author.

@@

\subsection{Software functionalities}\label{sec:functionalities}

\subsection{The \texttt{smuggle} statement}

\subsection{The onion comment}

\subsection{The \texttt{davos} config}

\subsection{Additional functionality}

% Present the major functionalities of the software.
